Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Edit Neuquen basin application
Not much to add here. Only commented about the magnitude of the
differences and how they are larger than the accuracy of most gravity
data.

We applied the new algorithms and optimal values of $D$ and $\delta$ determined
previously to calculate the gravitational effects of the Neuqu\'en Basin:
a sedimentary basin
located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude
(Fig.~\ref{fig:neuquen-basin}a).
The basin includes continental and marine siliciclastics, carbonates, and evaporites
accumulated over the Jurassic and the Cretaceous constituting a stratigraphic record up
to 5000m of depth \citep{Howell2005}.

@@

Finally, we computed the gravitational potential $V$ and the vertical component of the
gradient ($g_z$) on a computation grid of $159\times163$ nodes ($0.05^\circ$ spacing on
both longitude and latitude) at a 10km height over the mean Earth radius.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}c-d.
Moreover, we computed the differences between these fields and the ones generated by the
same model but now with a constant density as the mean value between -412kg/m$^3$ and
-275kg/m$^3$, and a linear density that assumes these two values on the highest and the
deepest point of the basin (Fig.~\ref{fig:neuquen-basin-densities}), respectively.
Fig.~\ref{fig:neuquen-basin-diffs}a-b and Fig.~\ref{fig:neuquen-basin-diffs}c-d show the
differences with the constant and the linear density, respectively.

>>>>

We applied the new algorithms and optimal values of $D$ and $\delta$ determined
previously to calculate the gravitational effects of the Neuqu\'en Basin,
a sedimentary basin located to the east of the Andes, between 32$^\circ$S and
40$^\circ$S latitude (Fig.~\ref{fig:neuquen-basin}a).
The basin includes continental and marine siliciclastics, carbonates, and evaporites
accumulated over the Jurassic and the Cretaceous constituting a stratigraphic record up
to 5000m of depth \citep{Howell2005}.

@@

Finally, we computed the gravitational potential $V$ and the vertical component of the
gradient ($g_z$) on a computation grid of $159\times163$ nodes ($0.05^\circ$ spacing on
both longitude and latitude) at a 10 km height over the mean Earth radius.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}c-d.

We computed the differences between the results for the exponential density function and
those generated by the same model but now with a constant density (the mean of
-412kg/m$^3$ and -275kg/m$^3$).
We also computed the differences between the exponential density and a linear density
that assumes these two values on the highest and the deepest point of the basin
(Fig.~\ref{fig:neuquen-basin-densities}).
Fig.~\ref{fig:neuquen-basin-diffs}a-b and Fig.~\ref{fig:neuquen-basin-diffs}c-d show the
differences with the constant and the linear density, respectively.
The maximum absolute difference in the computed $g_z$ is approximately 8 mGal for the
homogeneous case and approximately 6 mGal for the linear density case.
Both are well above the accuracy of data derived from spherical harmonic models, which
is often used for regional interpretations.
